Monte Carlo comparisons \\ VBSCAN Cost Action

### 2017-11-13 Setup/report.tex
changes of mathieu
added setup for NLOPS matchnig

\begin{document}
\maketitle

@@

\section{Codes}
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
        M. Pellen    &  {\sc Recola}\ +{\sc MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
        C. Schwan    &  {\sc BONSAY}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  Yes  &  No  &  No
    \end{tabularx}
    \caption{\label{tab:codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}

@@

The plan is: \\
- Scan in $m_{\Pj \Pj}$ and $|\Delta y_{\Pj \Pj}|$ at LO and compute the EW, QCD and interference (for the one who can) contribution. \\
The binning in $m_{\Pj \Pj}$ is $\left[ 0, 50, 100, ..., 450, 500, 600, 700, 800 \right] $. \\
The binning in $|\Delta y_{\Pj \Pj}|$ is $\left[ 0, 0.5, 1.0, 1.5, ..., 4.5, 5.0 \right] $. \\
- Based on this, define a ``control region'' and a ``signal region'' (should be the one we have identified already).
- Compute the QCD correction to QCD-induced and EW in these two regions.
- Add PS to these computations (for those who can).
- Add EW on top (probably only Mathieu).

@@

>>>>

\begin{document}
\maketitle
\tableofcontents

@@

\section{Codes}
\begin{table}
    \footnotesize
    \begin{tabularx}{\textwidth}{c|c|X|X|X|X|X}
        Contact person  &  Code  &  $\mathcal O(\alpha^6)$ $|s|^2/$ $|t|^2/|u|^2$  &  $\mathcal O(\alpha^6)$ interf.  &  Off-shell  &  NF QCD  &  EW corr. to $\mathcal O(\alpha^5\alpha_s)$  \\
        \hline
        \hline
        A. Karlberg  &  {\sc POWHEG}  &  $t/u$  &  No  &  Yes  &  No  &  No  \\
        M. Pellen    &  {\sc Recola}\ +{\sc MoCaNLO}  &  Yes  &  Yes  &  Yes  &  Yes  &  Yes  \\
        M. Rauch     &  {\sc VBFNLO}  &  Yes  &  No  &  Yes  &  No  &  No  \\
        C. Schwan    &  {\sc BONSAY}  &  $t/u$  &  No  &  Yes, virt. No  &  No  &  No  \\
        M. Zaro      &  {\sc MG5\_aMC}  &  Yes  &  Yes  &  No virt.  &  No  &  No
    \end{tabularx}
    \caption{\label{tab:codes} Summary of the different properties of the codes employed in the comparison.}
\end{table}

@@

The plan is: \\
- Scan in $m_{\Pj \Pj}$ and $|\Delta y_{\Pj \Pj}|$ at LO and compute the EW, QCD and interference (for the one who can) contribution. \\
The binning in $m_{\Pj \Pj}$ is $\left[ 0, 50, 100, ..., 450, 500, 550, 600, 650, 700, 750, 800 \right] $. These are 17 bins. \\
The binning in $|\Delta y_{\Pj \Pj}|$ is $\left[ 0, 0.5, 1.0, 1.5, ..., 4.5, 5.0 \right] $. These are 11 bins. \\
- Based on this, define a ``control region'' and a ``signal region'' (should be the one we have identified already).
- Compute the QCD correction to QCD-induced and EW in these two regions.
- Add PS to these computations (for those who can).
- Add EW on top (probably only Mathieu).

@@

\newpage
\section{Matching to parton shower}
Same setup and observables as for the fixed-order runs.\\

Tools:
\begin{itemize}
    \item VBFNLO + Herwig7: dipole vs angular-ordered shower, check also MC@NLO  vs Powheg matching
    \item MG5\_aMC: Pythia8 vs Herwig++
    \item Powheg + Pythia8
    \item Whizard + Pythia6 / Pythia8 (MLM merging)
    \item Phantom + Pythia
\end{itemize}

Comparisons are done after shower and hadronization. Hadrons are kept stable (no $\pi \to 2\gamma$ decay, no $B$ decay) in order not to have extra photons/leptons in the final state.\\
No underlying event is simulated.\\
QED radiation is disabled in the shower.\\
For Pythia8, the Monash tune (number 14) should be used.\\
All other parameters, in particular those for which particular settings need to be employed e.g. for consistency with the matching method, are free to be changed.
